\documentclass[9pt]{article}
\usepackage[BoldFont,SlantFont,CJKchecksingle]{xeCJK}
\setCJKmainfont[BoldFont=SimHei]{Adina}
\setCJKmonofont{Adina}% 设置缺省中文字体
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[]{hyperref}
\hypersetup{
    colorlinks=true,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=NavyBlue,%
    urlcolor=NavyBlue,
    breaklinks=true
}
\urlstyle{same}

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright

\pagenumbering{arabic}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[3]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
      {\url{#2}}\\ \smallskip 
      {\href{mailto:#3}{#3}}\\ \smallskip
		\end{center}
	\end{changemargin}
}

\newcommand{\jobtitle}[3]{
	\textbf{#1}, \emph{#2} \hfill \emph{#3}\\
}

\newcommand{\jobdescription}[1]{
	\begin{changemargin}{0.15in}{0.15in}
    \smallskip
		{#1}
    \medskip
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.25in}{-0.5in}
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{曲晓峰}{http://www.quxiaofeng.me}{xiaofeng.qu.hk@ieee.org}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{工作经验}

\begin{body}
  \vspace{14pt}

    \jobtitle{助理研究员(兼职)}{香港理工大学}{2013年六月 - 2014年二月}
    \jobdescription{
        I had been developing a virtual and physical interactive human body model system for the Institute of Textiles \& Clothing. A real-time 3D data collecting device was interfaced with python in order to customize virtual 3D human body model, which was rendering by Python and OpenGL.
    }

    \jobtitle{编辑助理（兼职）}{International Journal of Image and Graphics (国际图形图像杂志)\\}{2010年九月 - 2012年三月}
    \jobdescription{
        I work as an editor assistant for the chief editor. I oversaw the manuscript reviewing process including submitting and reviewing; made acceptance decisions based on associate editors' suggestions; and coordinated with the publishing house. I also organized special issues; communicated with AE and reviewers to make the reviewing process efficient and not jammed. In this nineteen months, five issues (from 2011 Jan to 2012 Jan) were published under my supervision, and a simple but efficient local journal management and reporting system was developed using Microsoft Access.
    }

	\jobtitle{助理研究员}{香港理工大学}{2008年四月 - 2010三月}
    \jobdescription{
        I had made some biometric systems based on 51soc/Cypress USB/ARM/DSP/FPGA. In four systems, I had been working as a core member.
    }

	\jobtitle{助教}{香港理工大学}{2010年秋季学期 - 2012年秋季学期}
    \jobdescription {
        COMP407 Computer Graphics (2010 Fall),
        COMP102 Enterprise Information Technology (2011 Spring), 
        COMP210 Discrete Structures (Taught by Visiting Professor Zheng Rong, 2011 Fall),  COMP435p Biometrics Authentication (2012 Spring), 
        ENG2003 Information Technology (2012 Fall)
    }

\end{body}

\medskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{教育背景}

\begin{body}
	\vspace{14pt}
	\textbf{Ph.D. Candidate --- Supervisor: Prof. David Zhang}{} \hfill \emph{Present}{} \\
	\emph{The Hong Kong Polytechnic University}, Hong Kong, China{} \\
	%Dissertation: ``Simplifying the Programming of Intelligent Environments'' (usability in smart homes)\\
  \medskip
	\textbf{M.S.E. Detection Technology \& Automatic Equipment}{} \hfill \emph{March 2008}{} \\
	\emph{The Shenyang University of Technology}, Shenyang, Liaoning, China{} \\
	\textbf{``Outstanding Thesis''}: ``Vision Based On-line Pipe Inner and Outer Wall Surface Inspection System''\\
    \textbf{``Outstanding Graduate''}\\
  \medskip
	\textbf{B.S.E. Electrical Information Engineering} \hfill \emph{July 2005} \\
    \emph{The Shenyang University of Technology}, Shenyang, Liaoning, China{} \\
    Thesis: ``Vision Based On-line Pipe Internal and External Wall Surface Inspection System''\\
    \textbf{``Outstanding Graduate''}\\
    \textbf{``Outstanding Final Year Project''}\\
\end{body}

\medskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Honors
\header{奖励与荣誉}

\begin{body}
	\vspace{14pt}	
    \textbf{第十届全国大学生课外学术科技作品竞赛挑战杯三等奖\\
    第八届辽宁省挑战杯金奖}\\
    沈阳工业大学 \hfill{} \emph{2007}\\
    \medskip
    \textbf{中国专利 \#200620168791.X}\\
    ``圆筒内外壁加工精度在线成像检测装置''\\
    \hfill{} \emph{2008年三月十二日授权}\\
    \medskip	
    \textbf{中国专利 \#200610155870.1}\\
    ``圆筒内外壁加工精度在线成像检测装置及在线成像检测方法''\\
    \hfill{} \emph{2009年六月十日授权}\\
    \medskip    
    \textbf{中国专利 \#20110362063.8}\\
    ``一种人体掌纹图像采集装置及处理方法'' \hfill{} \emph{2012年六月27日公布}
\end{body}

\end{document}
