% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{report}


%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0in}
\setlength{\hoffset}{-0.2in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{10in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}


%-----------------------------------------------------------
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{makebox}

\pagestyle{empty}
\raggedbottom
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands

\newcommand{\minitab}[2][c]{\begin{tabular}{#1}#2\end{tabular}}

\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}

\newcommand{\resheading}[1]{
\vspace{6pt}\begin{tabular*}{6.71in}{l@{\extracolsep{\fill}}}
        \large {\textbf{#1}} \\
        \Xhline{1.2pt}
\end{tabular*}\vspace{-2pt}}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.9in}{ll@{\extracolsep{\fill}}r}
        \hspace{0.15in} $\bullet$ \hspace{0.05in} & \textbf{#1} & #2 \\
        & \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-4pt}}

\newcommand{\ressubheadingtwo}[1]{
\begin{tabular*}{6.9in}{ll@{\extracolsep{\fill}}r}
        \hspace{0.15in} $\bullet$ \hspace{0.05in} & \textbf{#1}\\
\end{tabular*}\vspace{-4pt}}

\newcommand{\ressubheadingthr}[3]{
\begin{tabular*}{6.9in}{llr}
        \hspace{0.15in} $\bullet$ \hspace{0.05in} & \multicolumn{2}{p{6.54in}}{\textbf{#1}} \\
        & \textit{#2} & \textit{#3} \\
\end{tabular*}\vspace{-4pt}}
%-----------------------------------------------------------

\begin{document}

\begin{tabular*}{6.7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Dongmin Guo} \\
\#4, Department of Computing &  00852-64894128 \\
The Hong Kong Polytechnic University  & csdguo@comp.polyu.edu.hk \\
Hung Hom, Kowloon, Hong Kong & https://sites.google.com/site/guodongmin/ \\
\end{tabular*}
\\

\vspace{0.1in}

\renewcommand{\labelitemi}{$-$}
\renewcommand{\labelitemii}{$\ast$}
\leftmargini=12mm
\leftmarginii=6mm


\resheading{Education}
\begin{description}
\item
    \ressubheading{The Hong Kong Polytechnic University}{Hong Kong}{Ph.D, Department of Computing}{Apr. 2008 - May. 2011}
    \begin{itemize}
        \resitem{Thesis: Automatic Breath Signal Analysis and System Design for Medical Applications}
    \end{itemize}

\item
    \ressubheading{Northwestern Polytechnical University}{Xi'an, China}{M.A.Sc. Precise Instrument and Mechanics}{Sep. 2003 - Apr. 2006}
    \begin{itemize}
        \resitem{Thesis: Development and Implementation of E-nose Based on Smell-seeing Technique}
    \end{itemize}
\item
    \ressubheading{Northwestern Polytechnical University}{Xi'an, China}{B.A.Sc. Measurement and Control Technique and Instrument}{Sep. 1999 - Jul. 2003}
\end{description}

\resheading{Work Experience}
\begin{description}
\item
    \ressubheading{The Hong Kong Polytechnic University}{Hong Kong}{Research Assistant}{Jun. 2011 - Jan. 2012}
    \begin{itemize}
        \resitem{Be responsible for the data analysis of breath signals.}
        \resitem{Be responsible for the development of the breath analysis system for diabetes.}
    \end{itemize}
\item
    \ressubheading{Alcatel-Lucent}{Shanghai, China}{Software Engineer}{Apr 2006 - Apr. 2008}
    \begin{itemize}
        \resitem{Be responsible for the development and maintenance of API module of RNC (Radio Network Controller) , in UMTS(Universal Mobile Telecommunications System)}
        \resitem{Develop new features to solve the overload of RNC.}
    \end{itemize}
\end{description}


\resheading{Publications}
\begin{description}
\item \ressubheadingtwo{\bf{Journal Papers}}
\begin{enumerate}
        \item {\bf{Dongmin Guo}}, David Zhang, and Lei Zhang, ``Sparse representation-based classification for breath sample identification,'' Sensors and Actuators B, vol. 158, no. 1, pp. 43-53, 2011. (SCI, IF: 3.368)
        \item {\bf{Dongmin Guo}}, David Zhang, and Lei Zhang, ``An LDA based sensor selection approach used in breath analysis system,'' Sensors and Actuators B, vol. 157, no. 1, pp. 265-274, 2011. (SCI, IF: 3.368)
        \item Jane You, {\bf{Dongmin Guo}}, and Hongzhi Zhang, ``Medical biometric computing,'' Communications of the China Computer Federation, 05, 2011.
        \item {\bf{Dongmin Guo}}, David Zhang, Naimin Li, Lei Zhang, and Jianhua Yang, ``A novel breath analysis system based on electronic olfaction,'' IEEE Transactions on Biomedical Engineering, vol. 57, no. 11, pp. 2753-2763, 2010. (SCI, IF: 1.782)
        \item {\bf{Dongmin Guo}}, Jianhua Yang, and Bingxi Li, Analysis and design of smell-seeing electronic nose system. Chinese Journal of Sensors and Actuators, 2006 vol.19, no.3, 2006. (EI)
        \item {\bf{Dongmin Guo}}, Jianhua Yang, and Bingxi Li, Study of smell-seeing sensor array based on metalloporphyrins and its image analysis. Chinese Journal of Sensors and Actuators, vol.18, no.4, pp.794-797, 2005. (EI)
\end{enumerate}

\item \ressubheadingtwo{\bf{Conference Papers}}
\begin{enumerate}
        \item {\bf{Dongmin Guo}}, David Zhang, and Naimin Li, ``Monitor blood glucose levels via breath analysis system and sparse representation approach,'' IEEE Conference on Sensors, 2010. (EI)
        \item {\bf{Dongmin Guo}}, David Zhang, Naimin Li, Lei Zhang, and Jianhua Yang, ``Diabetes identification and classification by means of a breath analysis system,'' International Conference on Medical Biometrics, pp. 52-63, 2010. (EI)
        \item Haifen Chen, Guangming Lu, {\bf{Dongmin Guo}}, and David Zhang, ``An effective feature extraction method used in breath analysis,'' International Conference on Medical Biometrics, pp. 33-41, 2010. (EI)
    \end{enumerate}

\item \ressubheadingtwo{\bf{Papers with Underreview}}
\begin{enumerate}
        \item {\bf{Dongmin Guo}}, David Zhang, Guangming Lu, Zhimin Yang, and Darong Wu, ``Breath Signal Analysis of Healthy, Sub-healthy, and Diseased Samples and the Hierarchical Classification,'' Submitted to IEEE Transactions on Biomedical Engineering.
    \end{enumerate}
\end{description}

\resheading{Patent}
\begin{description}
\item \hspace{0.15in} {David Zhang and {\bf{Dongmin Guo}}, ``An apparatus and method for breath analysis'' (Pending)}.
\end{description}

\resheading{School Projects}
\begin{description}
\item
    \ressubheadingthr{Research of TCM (Traditional Chinese Medicine) diagnosis technique based on breath signal identification and analysis (External: NFSC, China)}{Major Investigator}{2009 - 2011}
    \begin{itemize}
        \resitem{Be responsible for the disease-related feature extraction technique, such as:
             \begin{itemize}
             \resitem{extracting geometric features in both time space and phase space}
             \resitem{extracting frequency features by DWT and HHT}
             \resitem{building mathematical models for odor signals}
             \resitem{selecting the principal and independent components by using PCA and ICA}}\end{itemize}
        \resitem{Be responsible for the investigation and development of the pattern recognition techniques for different medical applications, such as:
             \begin{itemize}
             \resitem{the development of SVR+GMM model for blood glucose evaluation of diabetics}
             \resitem{the improvement of SRC for disease identification}
             \resitem{the improvement of SVOR for the ordinal classification of diabetes samples}
             \resitem{the development of hierarchical classification for healthy, subhealthy, and diseased samples}}\end{itemize}
    \end{itemize}
\item
    \ressubheadingthr{Public healthcare welfare by computerized TCM (Traditional Chinese Medicine) diagnosis system (External: PPR (Public Policy Research), Hong Kong)}{Major Investigator}{2008 - 2010}
    \begin{itemize}
        \resitem{Be responsible for the system development for breath analysis:
             \begin{itemize}
             \resitem{developing a breath analysis system for disease identification}
             \resitem{developing a specific diabetes condition monitor to predict the blood glucose values}
             \resitem{exploiting a series of medical applications by using breath analysis, such as the prediction of blood glucose values, the evaluation of dialysis for end-stage renal failure patients, the monitor of physical condition for sub-healthy patients}}\end{itemize}
        \resitem{Be responsible for the data collection and signal analysis:
             \begin{itemize}
             \resitem{designing a series of standard breath collection procedures}
             \resitem{analyzing breath signals from both frequency domain and time domain and designing various feature extraction methods for odor signals}}\end{itemize}
        \resitem{Be responsible for the investigation of sensor selection techniques:
             \begin{itemize}
             \resitem{investigating the current all sensor selection algorithms such as SFS, SBS, GA, etc}
             \resitem{developing an effective sensor selection approach by using LDA algorithm}}\end{itemize}
    \end{itemize}
\item
    \ressubheadingthr{Design and Development a Gas Detection Device Based on Smell-seeing Technique}{Principal Investigator}{2004 - 2005}
    \begin{itemize}
        \resitem{``Seed Fund'' of research students development projects of Northwestern Polytechnical University, granted a maximum fund.}
        \resitem{Be responsible for the set up of experiment platform}
        \resitem{Be responsible for the design of sensors}
        \resitem{Be responsible for the design algorithm for image process and transplanting the algorithm in Linux platform}
        \resitem{The project was evaluated as {\bf{\itshape{EXCELLENT}}}, 3 out of 56.}
    \end{itemize}
\end{description}

\resheading{Teaching Assistant}
\begin{description}
\item
    \ressubheadingthr{Computer Image Generation and Applications}{Department of Computing, The Hong Kong Polytechnic University}{Fall, 2009}
    \begin{itemize}
        \resitem{1 hour per week for 14 weeks.}
        \resitem{Be responsible for tutoring the experiments.}
    \end{itemize}
\item
    \ressubheadingthr{Biometric Authentication}{Department of Computing, The Hong Kong Polytechnic University}{Winter, 2008}
    \begin{itemize}
        \resitem{1 hour per week for 14 weeks.}
        \resitem{Provide tutorial on assignments.}
    \end{itemize}
\end{description}

\resheading{Awards}
\begin{description}
\item
    \ressubheadingthr{My master thesis is awarded ``The Excellent Master Thesis'' of NWPU}{Top 50 out of 2000 students}{Apr, 2006}
\item
    \ressubheadingthr{Awarded ``Excellent graduate'' of Shaanxi Province}{Top 100 out of about 10000 students}{Dec, 2005}
\item
    \ressubheadingthr{My work ranked 2nd in the ``CHALLENGE CUP'' of National Scientific Design Competition}{Top 200 out of 793 teams}{Nov, 2005}
\item
    \ressubheadingthr{``Top Ten Science and Technology Star'' of NWPU}{Top 10 out of about 5000 students}{Oct, 2005}
\item
    \ressubheadingthr{Awarded ``Chengfei'' Scholarship}{Top 10 out of 400 students}{Sep, 2005}
\item
    \ressubheadingthr{Excellent Research Student Scholarship of NWPU}{Top 20 out of 200 students}{Sep, 2005}
\item
    \ressubheadingthr{My academic paper ranked 1st in the ``JIU TIAN'' Academic Papers Competition for Postgraduate of NWPU}{Top 5 out of 52 candidates}{Jul, 2005}
\item
    \ressubheadingthr{My work ranked 1st in the ``CHALLENGE CUP'' of Scientific Design Competition of Shaanxi Province}{Top 4 out of 210 teams}{Jun, 2005}
\item
    \ressubheadingthr{My work ranked 2nd in the ``SAN HANG CUP'' of Scientific Design Competition of NWPU}{Top 5 out of 129 teams}{Apr, 2005}
\item
    \ressubheadingthr{Excellent Research Student Scholarship of NWPU}{Top 20 out of 200 students}{Sep, 2004}
\item
    \ressubheadingthr{Our team ranked 2nd in the Summer Social Practice Competition of NWPU}{Top 30 out of 83 teams}{Sep, 2004}
\end{description}

\resheading{Activities}
\begin{description}
\item \hspace{0.15in} {\bf{Journal Reviewer:}}
Sensors, International Journal of Image and Graphics
\end{description}

\resheading{Skills}
\begin{description}
\item \hspace{0.15in} {\bf{Languages:}}
C/C++ and MatLab
\item \hspace{0.15in} {\bf{Miscellaneous:}}
Fluent in spoken and written English, high responsibility, independence, quick learning, self-motivated, and good team skill
\end{description}

\resheading{Interests}
\begin{description}
\item \hspace{0.15in} {\bf{Academic:}} Pattern recognition, image processing, disease diagnosis, biometrics, and bioinformatics
\item \hspace{0.15in} {\bf{Personal:}} Hiking and photographing
\end{description}

\end{document} 